\documentclass[a4paper,12pt]{article}

\pagestyle{empty}
% Cribbed from:
%   http://www.inf.ed.ac.uk/resources/labs/eyetrack/consent_form.html

\usepackage{mathptmx}
\usepackage[margin=4cm]{geometry}

\begin{document}
\begin{center}
  {\huge \textbf{Informed consent form for experimental participants}}
\vspace{1cm}

\textit{Please read the following information carefully. You may also
  request a copy for future reference.}
\end{center}

\textsc{Description}: You are invited to participate in a research
study on how quickly people can respond to stimuli under different
conditions. In this experiment, you will play a simple game in which
you have to press a button as quickly as possible under different
conditions, and receive a score that depends on how quickly

\textsc{Risks and Benefits}: Beyond pleasure derived by way of
participating in an experiment, there are no benefits to
participation. There are no risks beyond the usual risks involved in
using a computer.

\textsc{Time involvement}: Your participation in this experiment will
take approximately \underline{\hspace{2em}} minutes.

\textsc{Subject's rights}: If you have read this form and have decided
to participate in this project, please understand your participation
is voluntary and you have the right to withdraw your consent or
discontinue participation at any time without penalty. You have the
right to refuse to answer particular questions. Your individual
privacy will be maintained in all published and written data resulting
from the study.

If you agree with the above-stated conditions and are willing to
participate in the experiment, please continue. By continuing, you
agree that you meet the following conditions:
\begin{itemize}
%\item You are a native speaker of English.
\item You are over 18 years old.
\item You have read the above consent form, understood it and you agree to it.
\item You want to participate in the above-mentioned experiment.
\end{itemize}
\vfill
\hfill
SFRT
\end{document}
